---
title: "Bachelor analysis"
author: "Maria"
date: "28/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
```

Packages

```{r}
#load packages
pacman::p_load(tidyverse, lme4, lmerTest, rethinking)


```

Load data

```{r}
#read experimental data (run in one go)
setwd("C:/Users/maria/OneDrive/Dokumenter/Uni/Bachelor/Bachelor Analysis/finalpavdata")

pavlovia <- list.files(path = "C:/Users/maria/OneDrive/Dokumenter/Uni/Bachelor/Bachelor Analysis/finalpavdata",  
                       pattern = "*.csv") %>% 
  map_df(~read_csv(.))
```


```{r}
#read survey data
qual <- read_csv("finalqualdata.csv")  

```

Fix the same IDs occuring for different participants

```{r}
#check to see if participants have the same id
# df %>%
#   group_by(id) %>%
#   dplyr::summarise(Count = n()) 


#16727 -
#8024 -
#8083 -
#1349 -

#13149 has started over 

#separate participants with the same randomly generated ID 

#participant 16727
id_16727_1 <- pavlovia %>% 
  filter(id == "16727") %>% 
  filter(date == "2021-11-04_16h06.00.374") %>% 
  mutate(id = ifelse(id == 16727, 111111, NA)) #give new id

id_16727_2 <- pavlovia %>% 
  filter(id == "16727") %>% 
  filter(date == "2021-10-13_15h58.51.979") %>% 
  mutate(id = ifelse(id == 16727, 222222, NA)) #give new id

#next participant 8024
id_8024_1 <- pavlovia %>% 
  filter(id == "8024") %>% 
  filter(date == "2021-10-29_07h55.44.902") %>% 
  mutate(id = ifelse(id == 8024, 333333, NA)) #give new id

id_8024_2 <- pavlovia %>% 
  filter(id == "8024") %>% 
  filter(date == "2021-10-25_15h47.07.921") %>% 
  mutate(id = ifelse(id == 8024, 444444, NA)) #give new id


#filter out participants from main dataframe
pavlovia <- pavlovia %>% 
  filter(id != 16727) %>% 
  filter(id != 8024)

#rowbind the data to add the participants again
pavlovia <- rbind(pavlovia, id_16727_1)
pavlovia <- rbind(pavlovia, id_16727_2)
pavlovia <- rbind(pavlovia, id_8024_2)
pavlovia <- rbind(pavlovia, id_8024_1)


#----------
#again separate participants with the same randomly generated ID but in the qualtrics dataframes

#participant 16727
qual16727_1 <- qual %>% 
  filter(id == "16727") %>% 
  filter(RecordedDate == "2021-11-04 09:35:31") %>% 
  mutate(id = ifelse(id == 16727, 111111, NA)) #give new id

qual16727_2 <- qual %>% 
  filter(id == "16727") %>% 
  filter(RecordedDate == "2021-10-13 08:19:03") %>% 
  mutate(id = ifelse(id == 16727, 222222, NA)) #give new id

#participant 8024
qual8024_1 <- qual %>% 
  filter(id == "8024") %>% 
  filter(RecordedDate == "2021-10-29 00:59:32") %>% 
  mutate(id = ifelse(id == 8024, 333333, NA)) #give new id

qual8024_2 <- qual %>% 
  filter(id == "8024") %>% 
  filter(RecordedDate == "2021-10-25 08:34:42") %>% 
  mutate(id = ifelse(id == 8024, 444444, NA)) #give new id

#filter out participants from survey dataframe
qual <- qual %>% 
  filter(id != "16727") %>% 
  filter(id != "8024")

#rowbind the data to add the participants again
qual <- rbind(qual, qual16727_1)
qual <- rbind(qual, qual16727_2)
qual <- rbind(qual, qual8024_1)
qual <- rbind(qual, qual8024_2)


```

Merge data

```{r}
#merge pavlovia and survey
merged <- merge(pavlovia, qual)

#filter out false session
merged <- filter(merged, !EndDate == "2021-10-05 07:12:27")

#read and write the merged dataset
#write_csv(merged, "merged.csv") 
#read_csv("merged.csv")

```

Clean dataframe

```{r}
#read full dataframe
df <- merged %>% 
  filter(anagrams != "remove" | is.na(anagrams)) #remove false anagrams while keeping trials without anagrams


#remove participants and trials based on exclusion criteria and errors
df <- subset(df, !is.na(df$RT)) %>% #remove missing reaction times
  subset(Att_disease != "Ja") %>% #remove attentional disorders
  subset(Pregnant != "Ja") %>% #remove recent pregnancy 
  subset(Hormonal_disease != "Ja") %>% #remove hormonal diseases
  #subset(HC_time != "Under 3 måneder") %>% #done manually below 
  subset(Age_1 < 40) %>% 
  subset(Gender != "Mand") %>% 
  subset(id != 675) %>% #remove the specific participants under 3 months on HC
  subset(id != 3716) %>% #remove the specific participants under 3 months on HC
  subset(id != 13149) #remove the specific participants under 3 months on HC

#filter(!str_detect(tolower(HC_time), pattern = "under")) #same problem but the manual solution above works


#keep only relevant columns
df <- subset(df, select = c(id, anagram_answer, RT, anagrams, correct, IQresponse.keys, IQresponse.corr, options, CorrectIQ, Gender, Age_1, HC_use, HC_ever, HC_time, Time_since_use, Previous_HC_Time, HC_type, HC_type_8_TEXT, Brand, Generation, Pregnant, Hormonal_disease, Days_since_last_mens, Length_of_cycle, Prediction_ability_1, Att_disease, Dyslexic, Education, IQ_abilities_1, IQ_abilities_2, IQ_abilities_3, Difficulty_1, Difficulty_2, Social_setting, Height_1, Weight_1, OC_cycle, IUD, IUD_time_1, previous_HC, previous_HC_type, why_change_HC, Previous_HC_cancel, HC_sideeffects, Sexuality, Sexual_orientation, Partner, Children, Psych_comorbidity, Medication_depress, Medication_anxiety, Smoking, Alcohol_use, Alcohol_weekly, Alcohol_craving_1, Alcohol_crav_1, Alcohol_crav_2, Alcohol_crav_3, Alcohol_crav_4, Alcohol_crav_5, Alcohol_crav_6, Alcohol_crav_7, Alcohol_crav_8, Alcohol_crav_9, Alcohol_crav_10, Alcohol_crav_11, Alcohol_crav_12, Alcohol_audit1, Alcohol_audit2,Alcohol_audit3, Alcohol_audit4,Alcohol_audit5,Alcohol_audit6,Alcohol_audit7,Alcohol_audit8,Alcohol_audit9,Alcohol_audit10)) 



```

Make column for accuracy 

```{r}
#code accuracy column for both tasks
df <- df %>% 
  mutate(anagram_answer = ifelse(is.na(anagram_answer), "wrong", anagram_answer)) %>% #NAs count as wrong answers
  mutate(anagram_accuracy = ifelse(anagram_answer == correct, 1, 0)) %>% #1 for correct solutions, 0 for incorrect (referring to correct column)
  mutate(anagram_accuracy = ifelse(anagram_answer == "demoshow", 1, anagram_accuracy)) %>% #accept this as correct
  mutate(overall_accuracy = anagram_accuracy) %>% #copy the anagram accuracy to the overall accuracy
  mutate(overall_accuracy = ifelse(is.na(overall_accuracy), IQresponse.corr, anagram_accuracy)) %>% #add the IQ accuracy where we have missing info 
  mutate(overall_accuracy = ifelse(is.na(overall_accuracy), 0, overall_accuracy))


```

Make column for menstrual cycle

```{r}
#fix class
df <- df %>% 
  mutate(Days_since_last_mens = as.numeric(Days_since_last_mens)) %>% #numeric
  mutate(Length_of_cycle = as.numeric(Length_of_cycle)) #numeric
         
#calculate percentage and menstrual phases (rough estimate)
df <- df %>% 
  mutate(Percentage_cycle = (Days_since_last_mens/Length_of_cycle)*100) %>% #how far along in menstrual cycle
  mutate(Menstrual_phase = ifelse(Percentage_cycle >= 0 & Percentage_cycle <= 45, "follicular phase", NA)) %>%  #follicular phase
  mutate(Menstrual_phase = ifelse(Percentage_cycle > 45 & Percentage_cycle <= 55, "ovulation", Menstrual_phase)) %>%  #ovulation 
  mutate(Menstrual_phase = ifelse(Percentage_cycle > 55, "luteal phase", Menstrual_phase)) %>%  #luteal phase
  mutate(Menstrual_phase = ifelse(is.na(Menstrual_phase), "hormonal group", Menstrual_phase)) #add the hormonal group to avoid NAs

#fix HC type currently including previous HC 
df <- df %>% 
  mutate(previous_HC_type = ifelse(previous_HC == "Ja", HC_type, NA)) %>% 
  mutate(HC_type = ifelse(HC_use == "Nej", NA, HC_type)) %>% 
  mutate(previous_gen = ifelse(HC_ever == "Ja", Generation, NA)) %>% 
  mutate(Generation = ifelse(HC_use == "Nej", NA, Generation))
  
```

Make column for task type

```{r}

df <- df %>% 
  mutate(Task = ifelse(is.na(anagram_accuracy), "IQ", "anagram")) %>%  #make task column
  mutate(Dyslexic = ifelse(Dyslexic == "Ja" & Task == "anagram", "remove", Dyslexic)) %>%  #remove dyslecix people in anagram tasks
  filter(Dyslexic != "remove")
  
```

Fix spelling 

```{r}
#correcting spelling mistakes etc in the brand column
df$Brand[df$Brand == "2"] <- NA
df$Brand[df$Brand == "2 gen"] <- NA
df$Brand[df$Brand == "2 generation"] <- NA
df$Brand[df$Brand == "2."] <- NA
df$Brand[df$Brand == "2. generation"] <- NA
df$Brand[df$Brand == "2 generation Malonetta"] <- "Malonetta"
df$Brand[df$Brand == "2. generations - Microgyn"] <- "Microgyn"
df$Brand[df$Brand == "2. generations p-piller (femicept)"] <- "Femicept"
df$Brand[df$Brand == "2. Generations, Microgyn (Stoppede på p-piller for 6 år siden))"] <- "Microgyn"
df$Brand[df$Brand == "2. genration Femicept"] <- "Femicept"

df$Brand[df$Brand == "3. generation"] <- NA
df$Brand[df$Brand == "Anastella"] <- "Anastrella"
df$Brand[df$Brand == "anastrella"] <- "Anastrella"
df$Brand[df$Brand == "femicept"] <- "Femicept"
df$Brand[df$Brand == "cilest"] <- "Cilest"

df$Brand[df$Brand == "Det er over 10 år siden"] <- NA
df$Brand[df$Brand == "Femicept, Mirabella (2. generation)"] <- "Femicept"
df$Brand[df$Brand == "fik altid de billigste. ved ikke hvilket mærke det er flere år siden"] <- NA
df$Brand[df$Brand == "Gestinyl lyder bekendt (mere end 4 år siden)"] <- NA
df$Brand[df$Brand == "leverette"] <- "Leverette 21"
df$Brand[df$Brand == "Leverette 21 (indeholder levonorgestrel./ethinylestradiol"] <- "Leverette 21"
df$Brand[df$Brand == "Leverette 21 Ethinylestr + Levonorgest"] <- "Leverette 21"

df$Brand[df$Brand == "Det billigste på apoteket (forskelligt fra gang til gang)"] <- NA
df$Brand[df$Brand == "jeg har ingen ide, jeg tog sidst piller for 5 år siden"] <- NA
df$Brand[df$Brand == "Mercilon / denise / femistad"] <- "Mercilon"
df$Generation[df$Generation == "Ved ikke"] <- NA

df$HC_type[df$HC_type == "Hvis andet, hvad:"] <- "P-ring" #from assessing submitted answer
df$IUD[df$IUD == "Ved ikke/kan ikke huske"] <- NA

df$Brand[df$Brand == "malonetta"] <- "Malonetta"
df$Brand[df$Brand == "Malonetta, 2. generations"] <- "Malonetta"
df$Brand[df$Brand == "melonetta"] <- "Malonetta"
df$Brand[df$Brand == "2. generation Malonetta"] <- "Malonetta"
```


Shorten answers

```{r}
#shorten education names
df <- df %>% 
  mutate(Education = ifelse(Education == "Kort videregående uddannelse (fx erhvervsuddannelse på 2 år inkl praktik)", "Kort", Education)) %>% 
  mutate(Education = ifelse(Education == "Mellemlang videregående uddannelse (fx bachelor)", "Mellemlang", Education)) %>% 
  mutate(Education = ifelse(Education == "Lang videregående uddannelse (fx kandidat el. PhD)", "Lang", Education)) %>% 
  mutate(Education = ifelse(Education == "Anden uddannelse (under 2 år)", "Anden kort", Education)) %>% 
  mutate(Education = as.factor(Education))

#shorten answers
df <- df %>% 
  mutate(Social_setting = ifelse(Social_setting == "Nej, jeg sad alene og løste opgaverne", "Nej", "Ja")) %>% 
  mutate(OC_cycle = ifelse(OC_cycle == "Ja, jeg har taget eller skal tage min p-pille i dag", "Aktiv pille-dag", OC_cycle)) %>% 
  mutate(OC_cycle = ifelse(OC_cycle == "Nej, jeg holder pause mellem to pakker lige nu", "Pause", OC_cycle)) %>% 
  mutate(OC_cycle = ifelse(OC_cycle == "Jeg er for nyligt helt stoppet på p-piller", "Pause", OC_cycle)) #feedback fra personen sagde at de lige var stoppet sidste uge
```

Outliers

```{r}
#fix class
df$RT <- as.numeric(df$RT)

#check outliers
m <- mean(df$RT) #define mean
sd <- sd(df$RT) #define standard deviation

#calculate outlier limits
out.u<-m+3*sd #upper boundary
out.l<-m-3*sd #lower boundary

out.u #upper limit 830
out.l


```


Define lower + upper limit and round RT

```{r}
df <- df %>% 
  mutate(RT = round(RT, digits = 2)) %>% 
  #mutate(AVG_IQ_Ability = round(AVG_IQ_Ability, digits = 2)) %>% 
  subset(RT >= 1) %>% #exclude unrealistic response times
  mutate(RT = ifelse(RT >= 830, 830, RT)) #define an upper limit and replace values exceeding it 
  
```

Fix classes and relevel

```{r}

#fix classes
df <- df %>% 
  mutate(HC_use = as.factor(HC_use)) %>% #make into factor
  mutate(HC_type = as.factor(HC_type)) %>% #make into factor
  mutate(Task = as.factor(Task))  #make into factor


#fix education levels
df$Education <- factor(df$Education, levels = c("Folkeskole", "Gymnasiel uddannelse", "Anden kort", "Kort", "Mellemlang", "Lang"))

#fix HC levels
df$HC_use <- factor(df$HC_use, levels = c("Nej", "Ja"))


```
Write and read csv


```{r}
# write.csv(df, "clean_bachelor.csv")
# 
# df <- read_csv("clean_bachelor.csv")


```

Modelling

```{r}
#log response time
df <- df %>%
  mutate(logRT = log(RT)) %>% 
  mutate(Age_1 = as.factor(Age_1)) %>% 
  mutate(OC_cycle = as.factor(OC_cycle))
#sufficent normality assessed using qq plots and other visual discriptives
```

Preliminary investigation

```{r}
#preliminary models

#menstrual phase
m0_mens <- lmer(logRT ~ 0 + Menstrual_phase +(1|id), data = df)

#social setting
m0_soc <- lmer(logRT ~ 0 + Social_setting +(1|id), data = df)

#hc type
m0_type <- lmer(logRT ~ 0 + HC_type +(1|id), data = df)
```

Response time models (variations run and compared using AIC)

```{r}
#response time models (perseverance)
#models commented out failed to converge


m1 <- lmer(logRT ~ 1 + HC_use + (1 |id), data = df)
# m2 <- lmer(logRT ~ 1 + HC_use + (1 |Menstrual_phase:id) + (1|Menstrual_phase), data = df)
# m3 <- lmer(logRT ~ 1 + HC_use + (1 |HC_type:id) + (1|HC_type), data = df)
# m4 <- lmer(logRT ~ 1 + HC_use + (1 |Menstrual_phase:id) + (1|Menstrual_phase) + (1 |HC_type:id) + (1|HC_type), data = df)


m5 <- lmer(logRT ~ 1 + HC_use + Education + (1 |id), data = df)
m6 <- lmer(logRT ~ 1 + HC_use + Education + (1 |Menstrual_phase:id) + (1|Menstrual_phase), data = df)
# m7 <- lmer(logRT ~ 1 + HC_use + Education + (1 |HC_type:id) + (1|HC_type), data = df)
# m8 <- lmer(logRT ~ 1 + HC_use + Education + (1 |Menstrual_phase:id) + (1|Menstrual_phase) + (1 |HC_type:id) + (1|HC_type), data = df)


m9 <- lmer(logRT ~ 1 + HC_use + Age_1 + (1 |id), data = df)
m10 <- lmer(logRT ~ 1 + HC_use + Age_1 + (1 |Menstrual_phase:id) + (1|Menstrual_phase), data = df)
# m11 <- lmer(logRT ~ 1 + HC_use + Age_1 + (1 |HC_type:id) + (1|HC_type), data = df)
# m12 <- lmer(logRT ~ 1 + HC_use + Age_1 + (1 |Menstrual_phase:id) + (1|Menstrual_phase) + (1 |HC_type:id) + (1|HC_type), data = df)


m13 <- lmer(logRT ~ 1 + HC_use + Education + Social_setting + (1 |id), data = df)
m14 <- lmer(logRT ~ 1 + HC_use + Education + Social_setting + (1 |Menstrual_phase:id) + (1|Menstrual_phase), data = df)
# m15 <- lmer(logRT ~ 1 + HC_use + Education + Social_setting + (1 |HC_type:id) + (1|HC_type), data = df)
# m16 <- lmer(logRT ~ 1 + HC_use + Education + Social_setting + (1 |Menstrual_phase:id) + (1|Menstrual_phase) + (1 |HC_type:id) + (1|HC_type), data = df)


m17 <- lmer(logRT ~ 1 + HC_use + Age_1 + Social_setting +(1 |id), data = df)
m18 <- lmer(logRT ~ 1 + HC_use + Age_1 + Social_setting +(1 |Menstrual_phase:id) + (1|Menstrual_phase), data = df)
# m19 <- lmer(logRT ~ 1 + HC_use + Age_1 + Social_setting + (1 |HC_type:id) + (1|HC_type), data = df)
# m20 <- lmer(logRT ~ 1 + HC_use + Age_1 + Social_setting + (1 |Menstrual_phase:id) + (1|Menstrual_phase) + (1 |HC_type:id) + (1|HC_type), data = df)


m21 <- lmer(logRT ~ 1 + HC_use + Education + Social_setting + Task + (1 |id), data = df)
m22 <- lmer(logRT ~ 1 + HC_use + Education + Social_setting + Task + (1 |Menstrual_phase:id) + (1|Menstrual_phase), data = df)
# m23 <- lmer(logRT ~ 1 + HC_use + Education + Social_setting + Task + (1 |HC_type:id) + (1|HC_type), data = df)
# m24 <- lmer(logRT ~ 1 + HC_use + Education + Social_setting + Task + (1 |Menstrual_phase:id) + (1|Menstrual_phase) + (1 |HC_type:id) + (1|HC_type), data = df)


m25 <- lmer(logRT ~ 1 + HC_use + Age_1 + Social_setting + Task +(1 |id), data = df)
m26 <- lmer(logRT ~ 1 + HC_use + Age_1 + Social_setting + Task +(1 |Menstrual_phase:id) + (1|Menstrual_phase), data = df)
# m27 <- lmer(logRT ~ 1 + HC_use + Age_1 + Social_setting + Task + (1 |HC_type:id) + (1|HC_type), data = df)
# m28 <- lmer(logRT ~ 1 + HC_use + Age_1 + Social_setting +Task + (1 |Menstrual_phase:id) + (1|Menstrual_phase) + (1 |HC_type:id) + (1|HC_type), data = df)


m29 <- lmer(logRT ~ 1 + HC_use + Education + Task + (1 |id), data = df)
m30 <- lmer(logRT ~ 1 + HC_use + Education + Task + (1 |Menstrual_phase:id) + (1|Menstrual_phase), data = df)
# m31 <- lmer(logRT ~ 1 + HC_use + Education + Task + (1 |HC_type:id) + (1|HC_type), data = df)
# m32 <- lmer(logRT ~ 1 + HC_use + Education + Task + (1 |Menstrual_phase:id) + (1|Menstrual_phase) + (1 |HC_type:id) + (1|HC_type), data = df)


m33 <- lmer(logRT ~ 1 + HC_use + Age_1 + Task + (1 |id), data = df)
m34 <- lmer(logRT ~ 1 + HC_use + Age_1 + Task + (1 |Menstrual_phase:id) + (1|Menstrual_phase), data = df)
# m35 <- lmer(logRT ~ 1 + HC_use + Age_1 + Task + (1 |HC_type:id) + (1|HC_type), data = df)
# m36 <- lmer(logRT ~ 1 + HC_use + Age_1 + Task + (1 |Menstrual_phase:id) + (1|Menstrual_phase) + (1 |HC_type:id) + (1|HC_type), data = df)


m37 <- lmer(logRT ~ 1 + HC_use + Education + Task + (1 + Task |id), data = df)
m38 <- lmer(logRT ~ 1 + HC_use + Education + Task + (1 + Task |Menstrual_phase:id) + (1|Menstrual_phase), data = df) #best model 
# m39 <- lmer(logRT ~ 1 + HC_use + Education + Task + (1 + Task |HC_type:id) + (1|HC_type), data = df)
# m40 <- lmer(logRT ~ 1 + HC_use + Education + Task + (1 + Task |Menstrual_phase:id) + (1|Menstrual_phase) + (1 + Task |HC_type:id) + (1|HC_type), data = df)


m41 <- lmer(logRT ~ 1 + HC_use + Age_1 + Task + (1 + Task |id), data = df)
m42 <- lmer(logRT ~ 1 + HC_use + Age_1 + Task + (1 + Task |Menstrual_phase:id) + (1|Menstrual_phase), data = df)
# m43 <- lmer(logRT ~ 1 + HC_use + Age_1 + Task + (1 + Task |HC_type:id) + (1|HC_type), data = df)
# m44 <- lmer(logRT ~ 1 + HC_use + Age_1 + Task + (1 + Task |Menstrual_phase:id) + (1|Menstrual_phase) + (1 + Task |HC_type:id) + (1|HC_type), data = df)

#AIC() best performing is m38

# #variations of the best model:
# m38.1 <- lmer(logRT ~ 1 + HC_type + Education + Task +(1 + Task |Menstrual_phase:id) + (1|Menstrual_phase), data = df) #HC type
# 
# m38.2 <- lmer(logRT ~ 1 + HC_use*Social_setting + Education + Task + (1 + Task |Menstrual_phase:id) + (1|Menstrual_phase), data = df) #interaction 

#m38 still the best

```

Accuracy model similar to the perseverance model
```{r}
#accuracy
m38_accuracy <- glmer(overall_accuracy ~ 1 + HC_use + Education + Task + (1 + Task |id), data = df, family = binomial (link = logit), control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))) #nested effect removed because it was too complex


```


Additional Analyses (post hoc)

```{r}
#investigations on HC time for combination pills and iud


#OC combination pill time
oc <- df %>% #make relevant subset
  subset(OC_cycle != is.na(OC_cycle))

#fix HC levels
oc$HC_time <- factor(oc$HC_time, levels = c("Mellem 3 og 6 måneder", "Mellem 6 måneder og 1 år", "1-3 år", "Mere end 3 år"))

#RT model
m_octime <- lmer(logRT ~ 1 +OC_cycle + HC_time + Task +(1|Education) +(1 + Task |Education:id), data = df)
summary(m_octime)

#accuracy for OC combination pill
m_octime_a <- glmer(overall_accuracy ~ 1 +OC_cycle + HC_time + Task +(1|Education) +(1 + Task |Education:id), data = oc, family = binomial)
summary(m_octime_a)


#IUD time
iud <- df %>% 
  subset(IUD != is.na(IUD)) #subset relevant data

iud$IUD_time_1 <- as.numeric(iud$IUD_time_1) #fix class
iud$IUD[iud$IUD == "Ved ikke/kan ikke huske"] <- NA #make NA

#RT model
m_iudtime <- lmer(logRT ~ 1 + IUD +IUD_time_1 + Task + (1|Education) +(1 + Task |Education:id), data = iud)
summary(m_iudtime)

#accuracy for IUD
m_iudtime_a <- glmer(overall_accuracy ~ 1 + IUD +IUD_time_1 + Task + (1|Education) +(1 + Task |Education:id), data = iud, family = binomial)
summary(m_iudtime_a)

```

Plotting

```{r}
#plotting

#boxplots
df %>% 
  ggplot() +
  aes(x = Education, y = RT, color = HC_use) +
  geom_boxplot() +
  theme_minimal() +
  scale_color_brewer(palette="Accent")

df %>% 
  ggplot() +
  aes(x = HC_use, y = RT, fill = Task) +
  geom_boxplot() +
  theme_minimal() +
  scale_fill_brewer(palette="YIGnBu") +
  labs(x = 'Hormonal Contraceptive Use', y = 'Response Time (seconds)', fill = 'Task Type')

oc %>% 
  ggplot() +
  aes(x = HC_time, y = RT, color = HC_time) +
  geom_boxplot() +
  theme_minimal() 


#bar plot overall
#perseverance
ggplot(df, aes(x = Task, y = logRT, fill = HC_use))+
  geom_bar(stat = 'summary', fun.y = mean, width = 0.4, position = 'dodge')+
  geom_errorbar(stat = 'summary', fun.data = mean_se, width = 0.4, position = 'dodge2')+
  labs(x = 'Task Type', y = 'Mean Logged Response Time', fill = 'Group')+
  scale_fill_brewer(palette = 'Greens')+ #YIOrRd
  scale_y_continuous(breaks = pretty_breaks())+
  ggtitle('Perseverance Investigation') +
  theme_minimal()

#performance
ggplot(df, aes(x = Task, y = overall_accuracy, fill = HC_use))+
  geom_bar(stat = 'summary', fun.y = mean, width = 0.4, position = 'dodge')+
  geom_errorbar(stat = 'summary', fun.data = mean_se, width = 0.4, position = 'dodge2')+
  labs(x = 'Task Type', y = 'Proportion of Correct Answers', fill = 'Group')+
  scale_fill_brewer(palette = 'BuPu')+ #YIOrRd
  scale_y_continuous(breaks = pretty_breaks())+
  ggtitle('Performance Investigation') +
  theme_minimal()



#bar plot oc
#performance
ggplot(oc, aes(x = Task, y = RT, fill = HC_time))+
  geom_bar(stat = 'summary', fun.y = mean, width = 0.5, position = 'dodge')+
  geom_errorbar(stat = 'summary', fun.data = mean_se, width = 0.5, position = 'dodge2')+
  labs(x = 'Task Type', y = 'Mean Response Time (seconds)', fill = 'Time on Combination Pills')+
  scale_fill_brewer(palette = 'Accent')+ #BuGn?
  scale_y_continuous(breaks = pretty_breaks())+
  ggtitle(' ') +
  theme_minimal()


#line plot for IUD
as.factor(iud$id)

ggplot(iud, aes(IUD_time_1, RT, color = IUD)) + 
  geom_smooth(method = lm, alpha = 0.2) + 
  geom_point() +
  scale_color_brewer(palette = 'Greens')+
  labs(x = 'Time since insertion (months)', y = 'Response Time (seconds)', color = 'Type of IUD')+
  theme_minimal()


```






